NumLin: Linear Types for Linear Algebra

### 2019-04-09 write-up/paper/formal_system.tex
Fix for shepherding: accessible soundness result

\begin{theorem}
(The Fundamental Lemma of Logical Relations)
\[
    \forall \Theta, \Delta, \Gamma, e, t.\ \Theta; \Delta ; \Gamma \vdash e : t \Rightarrow
    \forall k.\ \den{}{k}{ \Theta; \Delta ; \Gamma \vdash e : t }
\]
\end{theorem}

>>>>

\begin{theorem}
(The Fundamental Lemma of Logical Relations)
\[
    \forall \Theta, \Delta, \Gamma, e, t.\ \Theta; \Delta ; \Gamma \vdash e : t \Rightarrow
    \forall k.\ \den{}{k}{ \Theta; \Delta ; \Gamma \vdash e : t }
\]

\end{theorem}

\subsubsection{Explanation}

If an expression is syntactically type-checked, then for an arbitrary number of
steps $k$, under any substitution $\theta$ of free fractional-permission
variables, linear variables $\gamma$ (with a suitable heap $\varsigma$) and
intuitionistic variables $\delta$, that suitable heap and expression
$(\varsigma, \theta(\delta(\gamma(e))))$ are in the computational
interpretation of the type of that expression $\C{k}{ \theta(t) }$.

The \emph{computational interpretation} is as defined before: a combination of
a frame rule on heaps (no interference), type-preservation and termination (in
$j < k$ steps) to either an error or a heap-and-expression, with the further
condition that if the expression is a syntactic value then it is also one
semantically.

It identifies executions that do no un- or ill-defined behaviours (e.g.\ adding
a boolean and an integer). Since our operational semantics explicitly models
deallocation, we now know no well-typed program will ever try to access
deallocated memory, establishing the correctness of our memory management
checking.

\subsubsection{Proof Sketch}
